---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# soilmesh
<!-- badges: start -->
```{r, echo = FALSE}
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
version <- gsub('-', '.', version)
```
![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
<!-- badges: end -->

This package houses the functions I use for processing 3D meshes in ASI 468. This code has been kept separate from that in **diRtscience** because the mesh processing is very specific to my project, and it is not likely anyone else would need to use the functions in this package. I do plan to publish **diRtscience** on CRAN, so I want to be a good curator of that package and keep my niche stuff out of it. 
